### 2021-04-08 input/introduction.tex
add a todo
fix biblio, first names and duplicated entries
new comment

There is an ongoing evlution of storing data from the cloud to the
edges of the network. Either because it is where it has been created
and it is too expensive to be transmitted through the network, or
because it has been replicated to bring data closer to the end users
~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, the design and the development of building
blocks to manage data sets across Edge infrastructures have been
investigated for the last few years \cite{confais2017performance,
  confais2017object, fogstore, hasenburg2020towards}.  Although these systems,
provide good properties such as favouring network traffic confinement
by writting data locally, determining the location where to get the
content might be more expensive than retrieving the content itself.
%
Indeed, those systems, when not using a centralized index stored in a
Cloud, rely on a Distributed Hash Table (DHT) across the different
peers composing the infrastructure: When a client wants to access a
specific content, it has to perform a request to a first node to
determine from which site it will retrieve the content. Once it has
retrieved the content from the location it selected, a local replica
is created to improve the performance for future accesses and the
server in charge of maintaining the index is updated to reflect this
new location.
%
Accessing a remote node to find the location of an object (or one of
its copies) has many drawbacks: (i) The \textit{lookup penalty:} the
network latency to reach this remote node incurs an additional delay
to get the object, before being able to start its
downloading~\cite{asrese2019measuring, doan2019tracing}, (ii)
Answering external queries increases the load on the remote node,
potentially impacting its performance, (iii) It prevents nodes to
access objects in case of network partitioning: if the node in charge
of maintaining the object locations is isolated from the rest of the
infrastructure, nodes cannot access the object replicas even if some
would be reachable.

@@

@@

We evaluated our protocol through simulations using \textit{Peersim}~\cite{montresor2009peersim}. The topolgies we simulated are based on real-world ones from the Internet Toplogy
Zoo~\cite{topology-zoo}.  Our evaluation shows that \NAME is able to
provide a similar localization service when compared to a DHT-based
approach while removing the lookup penalty or to an hypothetical complete and robust broadcast. This directly translates
into faster data access as shown by our measurements, with a time
reduction from $20\%$ to $60\%$, depending on the sizes of the
objects. %\AVK[Talk about load balancing and traffic containment here]
We also show that by slightly delaying the sending of messages, \NAME
can match the number of messages of a DHT-based approach, at the cost
of a moderate increase in message sizes.

>>>>

There is an ongoing evlution of storing data from the cloud to the
edges of the network. Either because it is where it has been created
and it is too expensive to be transmitted through the network, or
because it has been replicated to bring data closer to the end users
~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, the design and the development of building
blocks to manage data sets across Edge infrastructures have been
investigated for the last few years \cite{confais2017performance,
  confais2017object, fogstore, hasenburg2020towards}.  Although these systems,
provide good properties such as favouring network traffic confinement
by writting data locally, determining the location where to get the
content might be more expensive than retrieving the content itself.
%
Indeed, those systems, when not using a centralized index stored in a
Cloud, rely on a Distributed Hash Table (DHT) across the different
peers composing the infrastructure: When a client wants to access a
specific content, it has to perform a request to a first node to
determine from which site it will retrieve the content.
\TODO{Add something about the fact that in addition to the location service of the replica, we need a service that maintain a view of the infrastructure topology so that each node can infer which replica is the closest one.}

Once it has
retrieved the content from the location it selected, a local replica
is created to improve the performance for future accesses and the
server in charge of maintaining the index is updated to reflect this
new location.
%
Accessing a remote node to find the location of an object (or one of
its copies) has many drawbacks: (i) The \textit{lookup penalty:} the
network latency to reach this remote node incurs an additional delay
to get the object, before being able to start its
downloading~\cite{asrese2019measuring, doan2019tracing}, (ii)
Answering external queries increases the load on the remote node,
potentially impacting its performance, (iii) It prevents nodes to
access objects in case of network partitioning: if the node in charge
of maintaining the object locations is isolated from the rest of the
infrastructure, nodes cannot access the object replicas even if some
would be reachable.

@@

\TODO{Explain that the problem can be seen as a graph partitioning problem}

@@

We evaluated our protocol through simulations using \textit{Peersim}~\cite{montresor2009peersim}. The topolgies we simulated are based on real-world ones from the Internet Toplogy
Zoo~\cite{knight2011internet}.  Our evaluation shows that \NAME is able to
provide a similar localization service when compared to a DHT-based
approach while removing the lookup penalty or to an hypothetical complete and robust broadcast. This directly translates
into faster data access as shown by our measurements, with a time
reduction from $20\%$ to $60\%$, depending on the sizes of the
objects. %\AVK[Talk about load balancing and traffic containment here]
We also show that by slightly delaying the sending of messages, \NAME
can match the number of messages of a DHT-based approach, at the cost
of a moderate increase in message sizes.
